Algorithmic model for N-GREEN optical ring

### 2017-11-23 Papier NGreen/model.tex
tex

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{graphicx,graphics} 
\usepackage{hyperref}

@@

\section{Model}
  \label{model}
  \subsection{Optical ring}
    Graphe oriente representant un anneau, definition des terme delay
  \subsection{Discrete time model}
    temps slotte correspondant a un tick d'horloge
  \subsection{Into the node : Two kind of traffics}
    Descripion buffers/ on prepare des conteneurs.definition des therme paquet slot buffers
    Description CRAN-BE, precision sur le modele de generation
    presentation des differentes politiques d'insertion.

  \subsection{Objectives}
    Etudier Le comportement de nos politiques
    Trouver une solution deterministe et etudier l'impact sur les BE

@@

\section{Deterministic approach for 0 latency on CRAN}
\label{det}
  \subsection{Packing}
  \subsection{Spreading}
  Pour ces deux la, ecrire proprement les ``algos''
  \subsection{Impact on the BE}
  REsultats de simuls

\begin{center}

      \includegraphics[width=\textwidth]{emission_antenna.pdf}

\end{center}

	Then, we call the \texttt{insert\_packets()} function to send the packets on the ring, if needed (i.e, if some CRAN has been generated, or the BE buffer is large, or old enough).
	Finally, the function \texttt{rotate\_ring()} is called, and every struct packets of the circular ring takes the following position in the table (the last cell of the table take the position 1).
	Afterwards, we call the \texttt{remove\_packets()} function, that free the reading\_slot of a node, if the packet on it has been sent by this node.
	\subsection{BE-Generation}
	The best effort generation follows the SBBP decribed in sec~\ref{model}. Since the batch process have, at the most 10 states, this functions runs in $O(1)$: one random drawing for the transition in the markov chain, another random drawing for the batch process, and the Inverse transform sampling, which is bounded by the number of states.
	\subsection{CRAN-Generation}
	We splitted the CRAN-Generation in two steps. First, the nodes which are not the BBU adds their messages from antennas to buffers, if needed. In a second time, the BBU generates and answer in it's buffer, if there is a CRAN packet in the reading\_slot of the BBU.
	\subsection{Insertion packet}
	A node emits a packet on the ring, in its writting\_slot, if :
\begin{itemize}
\item In no management mode :  if the size of the buffer is greater or equal to $\beta .Q $ ($\beta \in ]0;1] , Q$ is the size of the buffer) , or if the oldest datas has arrived in the buffer before or to $t-\alpha$, ( $t$ is the current slot, and $\alpha$ is the deadline, expressed in slot).
\item In CRAN priority mode : 
	\begin{itemize}
	\item If the BE-buffer satisfy one of the latter condition,
	\item Or if there is some CRAN in the CRAN\_buffer. The packet emitted contains all the CRAN possible, filled with as much BE as possible. 
	\end{itemize}
\item in reservation mode, the slot on the writting\_slot of the node must be not reserved, or reserved for the node. Then the constraints are the same than the CRAN-priority mode.
\end{itemize} 	
\subsection{Slot Reservation}
In reservation mode, the main challenge is to reserve the slots for the nodes. Indeed, if a nodes $i$ needs the slot in his wrtting\_slot at time $t$, this slot needs to be reserved at time $t - size\_ring$ by $i$. In this situation, if the slot is already taken by a packet which has been sent by the node $k$, $k$ will remove the packet of the slot during the next lap of the ring, and no other nodes are able to write in this slot before it cames back to the node $i$ a date $t$.

@@

The application we study takes place in the C-Ran context. We want to centralise calculations into a common data-center for an area of antennas distributed on the territory. The data between the RRH (antennas) and the BBU (data-center) are transiting through an optical ring. We study here only the behaviour of the ring. First, for an easier model, we consider a ring in which one or two nodes are the data-centers, and the other nodes of the ring sends some data coming from the RRH.

Every millisecond, between each couple RRH-BBU, the following periodic process is observed:
\begin{enumerate}
 \item The RRH sends some latency critical data to its BBU.
 \item Those data are transferred to the BBU through the ring .
 \item After a computation time of the message, the BBU sends an answer to its RRH.
\end{enumerate}
 This periodic process has a critical end to end latency, thus a messages has to be as little buffered as possible before being sent in the ring.
 Every messages will browse the entire ring during the process. Since the ring is approximately 50km long, a messages needs $250 \mu s$ to travel this length.
 Considering that the periodicity of the emissions ($1ms$) is greater than a ride of the ring, we take $P$ a multiple of the time needed to travel the ring.

\section*{Sending policy}
In the studied model, the nodes of the ring have a {\bf broadcast and select} policy. Then, the physical times needed to insert the data in the ring are negligible in regard of the other times.
When a node sends a packet on the ring, it contains data for several destinations. Every node of the ring reads all the slots and keep the data addressed to it. It copy the data of the packet in the slot, but does not remove anything. The only node that can free a slot is the one which send a packet in it.

%when a node sends some data in a slot, this slot is {\em taken} by this node for an entire ride of the ring. This means that every nodes of the ring can collect the information addressed to it, but it does not delete the data in the slot. The slot is fully cleared by the node that sent it, when it came back after a ride of the ring.

Thus, a node has to wait for a free slot before sending a packet in the ring. To avoid overloading the ring, a node sends a packet only if some criteria  are satisfied.
We define by $Q$ the capacity of the buffer of a node, $\alpha$ the {\em minimum load} of the buffer, $0 \leq  \alpha \leq 1$, and $\delta$ the {\em maximum delay}.

The node sends a packet in a slot if:
\begin{itemize}
 \item The amount of data $q$ in the buffer is greater than $\alpha . Q$,
 \item or the older data in the buffer is waiting for more than $\delta$.
\end{itemize}

The buffer of a node is filled with the FIFO rule by a traffic coming from external sources. Then, when the node has an available free slot, the packet is inserted in the slot if one of the previous constraints are satisfied. Otherwise the node does not send anything in the ring and wait for the next free slot.

\begin{center}

\end{center}

\section{C-RAN context}

In C-RAN context, this amount of data $q$ contains two kinds of data: the latency critical flow coming from RRH or BBU, and an other flow, called {\em best effort}.

We can consider two buffers containing $x$ and $y$ amount of data. The first one is filled with the C-Ran data in priority, and the best effort flow if needed, the second one takes the rest of best effort flow. We consider that, even if a lot of RRH are represented by a node on the ring, the amount of C-Ran data incoming to a node is strongly lower than the capacity of a packet ($\simeq 1.2$ Gbps for each RRH, 100 Gbps into the ring).
The C-RAN data comes periodically in regard of the period $P = 1ms$. 
The best effort data comes more randomly (can be modelled by a Poisson distribution, for example), and are inserted in the buffer if $x = 0$.

\begin{center}

\end{center}

\section*{Model}
We consider an optical ring composed of $k$ nodes ($k={3,...,10}$).
We are in a discrete time model: the time is split in $N$ slot, rotating to the following position each time step $t = 10 \mu s$. This value is the switching granularity.
\begin{center}

      \includegraphics[scale=0.5]{anneau1.pdf}
      \hspace{3cm}
      \includegraphics[scale=0.5]{anneau2.pdf}

\end{center}

Considering a length of 50 km for the ring, we evaluate the number of slots about 25 into the ring.

\section*{Study}
The purpose is here to reduce the latency of the C-RAN data. Two event can increase this latency: 
\begin{enumerate}
  \item The node has enough data $q$ to emit in the ring, but no slots are available.
 \item The node does not have enough data $q$ to emit and a data from $x$ is waiting for less than $\delta$.
\end{enumerate}

In a first time, we will look at the first problem, and try to determine from what load of the ring, the time taken to wait a free slot in the ring is too long.

>>>>

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{graphicx,graphics} 
\usepackage{hyperref} 
\usepackage{mathtools, bm}
\usepackage{amssymb, bm}

@@

\section{Model}
  \label{model}
  \subsection{Optical ring}
  Consider a directed circular graph $C_N$ representing an optical ring. $N$ is the number of nodes on the ring/the graph. Each arc $(u,v)$ is labeled by an integer distance $d(u,v)$ corresponding to the physical delay of the link in the ring, i.e. the time taken by a signal to go from $u$ to $v$ using this arc.

  \subsection{Message Granularity}
    The time is discretized. The unit of time is the {\bf time slot}. Each arc $(u,v)$ can be represented as a sequence of {\bf slots} $\{s_1, ... , s_k\}$, with $k = d(u,v)$. We denote by $s_n(u,v)$ the $n^{th}$ slot of the arc $(u,v)$. $s_i(v), i\in \{-d(u,v), ... , -1\} \cup \{1 , ... , d(v,w)\}$ is the $i^{th}$ slot after (before if $i<0$) v on the ring.
    On the following example, the red slot can be denoted by $s_2(u,v)$, $s_2(u)$ or $s_{-6}(v)$. 
    \begin{figure}[h]
    \centering
      \includegraphics[scale=0.5]{suv.pdf}

      \caption{A link $(u,v)$ represented as a sequence of slots}
  \end{figure}

  Each node $v$ has a reading access on $s_{-1}(v)$ and a writing access on $s_{1}(v)$. Those slots are named respectively the reading and writing slots of $v$. Thus, during a time slot, a node $v$ can insert a {\bf packet} on it's writing slot, if it is allowed to. We will define the right of the nodes later on this paper. Then, at the end of the time slot, each packets skip to the next slot. A packet emitted by a node $u$ on it's writing slot $s_1(u)$ will be available in reading for a node $v$ on it's reading slot $s_{-1}(v)$ $d(u,v) -1$  time slot later.
\begin{figure}[h!]
      \includegraphics[scale=0.5]{anneau1.pdf}
      \hspace{3cm}
      \includegraphics[scale=0.5]{anneau2.pdf}
      \caption{One rotation of the ring}
  \end{figure}
  \subsection{Broadcast and select policy}
  The ring follows a broadcast and select behavior. When a packet is inserted in a slot on the ring, by a node, no other nodes are able to write on this slot. This packets can contain some data from several nodes on the ring, that are able to read in the packet. The only node which has the right to remove the packet from the slot is the owner. This mean that every packet makes exactly one lap of the ring. Furthermore, to write on a slot, a node has to have an empty slot in it's writing slot.

    \subsection{CRAN Context}
    Our study takes place in the C-RAN context. The purpose is to centralise the calculation units of some antennas, distributed on the field. To each antenna, called RRH (Remote Radio Head), is associated a BBU (BaseBand Unit) in the datacenter.
      The periodic process is the following: each {\bf period $P$}, every RRH send some datas thought the ring to it's BBU, then, after a computation time in the BBU, this latter answers to the corresponding RRH. 
      The time between the emission of the message by the RRH and the reception of the answers by the same RRH is called {\bf process time} and must not be too large, considering some 5G standards.
      In this paper we will consider that all the BBU are grouped in the same node, called {\bf datacenter}, and that the antennas are distributed on the others node of the ring.

  \subsection{Into the node : Two kind of traffics}
    To build the packets that are sent in the ring, the nodes have to deal with two kinds of traffic: 
    \begin{itemize}
    \item The {\bf Best effort traffic}, representing the internet flow.
    \item The {\bf C-RAN traffic}, representing the high priority flow.
    \end{itemize}
    Let us denote {\bf BE-message} and {\bf CRAN-message} the unit of data of this flows. A packet is made of several BE-messages or CRAN-messages, and can be a combination of both kind of messages.
    The messages coming to a node are buffered, and the nodes send a packet with the messages if : 
     \begin{itemize}
    \item The oldest message has arrived on the buffer before $t - \alpha$, if  $t$ is the actual time.
    \item The fill rate of the buffer is greater or equal than $\beta$.
    \end{itemize}
    Those parameters $\alpha$ and $\beta$ are fixed by the network specification.

    \begin{figure}[h!]
        \begin{center}
      \includegraphics[scale=0.5]{insertionbuff.pdf}

      \caption{The packet creation buffer}
      \end{center}
  \end{figure}

This behavior is the basic one, the buffer of a node is filled following the FIFO rule by the BE and C-RAN traffics. Then, when the node has an available free slot, the packet is created and inserted in the slot if one of the previous constraints are satisfied. Otherwise the node does not send anything in the ring and wait for the next free slot.

    \begin{figure}[h!]
\begin{center}

     \caption{No management mode.}
\end{center}
  \end{figure}

  In order to improve the CRAN-messages latency, we first imagined the following solution. Each nodes have two buffers. One for the BE-messages, and one fore the CRAN-messages. When a node is able to send some messages on the ring, i.e. the slot on it's writing slot is free, the packet is filled with the CRAN-messages first.

    \begin{figure}[h!]
\begin{center}

     \caption{CRAN priorirty mode.}
\end{center}
  \end{figure}

 In the next section, one can find the experimental performance evaluation of those two modes which show that, even for the CRAN priority mode, when the network is loaded, the latency of the CRAN messages is not low enough.

 Thus, we propose a deterministic approach in which we set the first date at which the antenna starts to emit and then we reserve the slots needed for the CRAN-message by preventing the others node to write in those slots during the previous ring lap of the slot.

  \subsection{Objectives}
    The main challenge of our study is to improve the CRAN-messages latency, such that the process time does not exceed a given time ${\bf T_{max}} $ while not penalizing too much the BE-messages.

    To understand the deterministic algorithm, one must introduce the behavior of the antennas.
    \subsection{CRAN message generation}
    The antennas send some heavy packets in the network. First, those packets are carried to the node of the right through an electronic network. Thus, the node is able to transform an electronic packet of $10\mu s$ in an optical packet of $1\mu s$. This multiplexing is explained in (DOC).

        \begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.3]{slot1.pdf}
  \includegraphics[scale=0.3]{slot2.pdf}
     \caption{Electronic-optical interface.}

\end{center}
  \end{figure}
    Thus, an antenna can not send of the ring more than every $10\mu s$. This time is called $EP$ (Emission Period).
    We denote by $ET<P$ (Emission time) the time of the emission of an antenna. Thus, an antenna emits ET/EP packets on the ring, during a period $P$.

        \begin{figure}[h!]
\begin{center}

      \includegraphics[width=\textwidth]{emission_antenna.pdf}
     \caption{Antenna traffic on the ring.}

\end{center}
  \end{figure}
    \subsection{BE message generation}
    	The BE message flow is modeled with a Switch Bernoulli Batch Process (SBBP). Ajouter Doc et details

@@

\section{Deterministic approach for 0 latency on CRAN}
\label{det}
\subsection{Slot Reservation}
In reservation mode, the main challenge is to reserve the slots for the nodes. Indeed, if a nodes $i$ needs the slot in his wrtting\_slot at time $t$, this slot needs to be reserved at time $t - size\_ring$ by $i$. In this situation, if the slot is already taken by a packet which has been sent by the node $k$, $k$ will remove the packet of the slot during the next lap of the ring, and no other nodes are able to write in this slot before it cames back to the node $i$ a date $t$.

@@

  \subsection{Packing}
  \subsection{Spreading}
  Pour ces deux la, ecrire proprement les ``algos''
  \subsection{Impact on the BE}
  REsultats de simuls

	Then, we call the \texttt{insert\_packets()} function to send the packets on the ring, if needed (i.e, if some CRAN has been generated, or the BE buffer is large, or old enough).
	Finally, the function \texttt{rotate\_ring()} is called, and every struct packets of the circular ring takes the following position in the table (the last cell of the table take the position 1).
	Afterwards, we call the \texttt{remove\_packets()} function, that free the reading\_slot of a node, if the packet on it has been sent by this node.
	\subsection{BE-Generation}
	The best effort generation follows the SBBP decribed in sec~\ref{model}. Since the batch process have, at the most 10 states, this functions runs in $O(1)$: one random drawing for the transition in the markov chain, another random drawing for the batch process, and the Inverse transform sampling, which is bounded by the number of states.
	\subsection{CRAN-Generation}
	We splitted the CRAN-Generation in two steps. First, the nodes which are not the BBU adds their messages from antennas to buffers, if needed. In a second time, the BBU generates and answer in it's buffer, if there is a CRAN packet in the reading\_slot of the BBU.
	\subsection{Insertion packet}
	A node emits a packet on the ring, in its writting\_slot, if :
\begin{itemize}
\item In no management mode :  if the size of the buffer is greater or equal to $\beta .Q $ ($\beta \in ]0;1] , Q$ is the size of the buffer) , or if the oldest datas has arrived in the buffer before or to $t-\alpha$, ( $t$ is the current slot, and $\alpha$ is the deadline, expressed in slot).
\item In CRAN priority mode : 
	\begin{itemize}
	\item If the BE-buffer satisfy one of the latter condition,
	\item Or if there is some CRAN in the CRAN\_buffer. The packet emitted contains all the CRAN possible, filled with as much BE as possible. 
	\end{itemize}
\item in reservation mode, the slot on the writting\_slot of the node must be not reserved, or reserved for the node. Then the constraints are the same than the CRAN-priority mode.
\end{itemize}
